Identifying Factors That Affect Political Freedom Within the OECD

### 2020-11-25 paper/paper.Rmd
fixed issue

```{r setup, include = FALSE}
library(tidyverse)
library(kableExtra)
library(stargazer)
library(patchwork)
size <- 30

@@

knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message = FALSE, 
                      fig.width = 12, fig.height = 8)

@@

data <- data %>%
  filter(year > 2000, year < 2019, country %in% countries) %>% 
  group_by(country) %>%
  mutate_at(vars(-country),list(~ifelse(is.na(.), median(., na.rm = TRUE), .))) %>% 
# Iceland spent 0 so I needed to manually recode that
  mutate(military_spending_pct_of_gdp = replace_na(military_spending_pct_of_gdp, 0)) %>% 
  mutate(murder_per_mil_people = replace(murder_per_mil_people, country == "Mexico", 29.07),
         murder_per_mil_people = replace(murder_per_mil_people, country == "Chile", 4.4),
         murder_per_mil_people = replace(murder_per_mil_people, country == "Colombia", 25.34)) %>% 
         # https://en.wikipedia.org/wiki/List_of_countries_by_intentional_homicide_rate
         # these murder rates were not included in the gapminder but i didnt want to 
         # lose 3 important countries in LA
  relocate(polrights_fh) %>% mutate(polrights_fh = (8 - polrights_fh),
                                    military_spending_pct_of_gdp = military_spending_pct_of_gdp * 100)%>% 
  mutate(corruption_perception_index_cpi = (corruption_perception_index_cpi - 100) * -1)

@@

```{r fig.align="center", results='asis'}
stat <- function(df = data, x, rounding_digits = 2){

    x <- dplyr::enquo(x)
    df %>%
      dplyr::summarise(
                       Mean  = mean( !! x),
                     Median  = median( !! x),
                         Std = sd  ( !! x),
                         Min = min ( !! x),
                         Max = max ( !! x),
                       Range = max(!! x) - min(!! x) ) %>%
      dplyr::mutate_if(is.numeric, round, rounding_digits)
  }

data %>% 
  select(-country) %>% 
map(function(x){stat(x, df = data)}) %>% 
  bind_rows(.id = "Variable") %>% 
  mutate(Variable = replace(Variable, 
                            values = c("Political Rights", "Year", 
                                       "Corruption Perception", 
                                       "Education Expenditure", 
                                       "Electricity Use", 
                                       "Gini", 
                                       "Internet Users",
                                       "Life Expectancy", 
                                       "Labor Force Participation", 
                                       "Military Spending", 
                                       "Murders rate"))) %>% 
kable(
  format = "latex",
  booktabs = TRUE,
  escape = FALSE,
  longtable = TRUE,
 caption = "Descriptive Statistics")
```

>>>>

```{r setup}
library(tidyverse)
library(kableExtra)
library(stargazer)
library(patchwork)

size <- 30

@@

knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message = FALSE, 
                      fig.width = 12, fig.height = 8) 
```

```{r, cache=TRUE}

@@

data <- data %>%
  filter(year > 2000, year < 2019, country %in% countries) %>% 
  group_by(country) %>%
  mutate_at(vars(-country),list(~ifelse(is.na(.), median(., na.rm = TRUE), .))) %>% 
# Iceland spent 0 so I needed to manually recode that
  mutate(military_spending_pct_of_gdp = replace_na(military_spending_pct_of_gdp, 0), 
         year = as.numeric(year)) %>% 
  mutate(murder_per_mil_people = replace(murder_per_mil_people, country == "Mexico", 29.07),
         murder_per_mil_people = replace(murder_per_mil_people, country == "Chile", 4.4),
         murder_per_mil_people = replace(murder_per_mil_people, country == "Colombia", 25.34)) %>% 
         # https://en.wikipedia.org/wiki/List_of_countries_by_intentional_homicide_rate
         # these murder rates were not included in the gapminder but i didnt want to 
         # lose 3 important countries in LA
  relocate(polrights_fh) %>% 
  mutate(polrights_fh = (8 - polrights_fh),
                                    military_spending_pct_of_gdp = military_spending_pct_of_gdp * 100) %>% 
  mutate(corruption_perception_index_cpi = (corruption_perception_index_cpi - 100) * -1) %>% 
  ungroup()

@@

```{r fig.align="center", results='asis'}
stat <- function(x, df = data, rounding_digits = 2){

    x <- enquo(x)
    df %>%
      summarise(
                       Mean  = mean( !! x),
                     Median  = median( !! x),
                         Std = sd  ( !! x),
                         Min = min ( !! x),
                         Max = max ( !! x),
                       Range = max(!! x) - min(!! x) ) %>%
      mutate_if(is.numeric, round, rounding_digits)
}

data %>% 
  select(-country) %>% 
map(function(x){stat(x)}) %>% 
  bind_rows(.id = "Variable") %>% 
  mutate(Variable = replace(Variable, 
                            values = c("Political Rights", "Year", 
                                       "Corruption Perception", 
                                       "Education Expenditure", 
                                       "Electricity Use", 
                                       "Gini", 
                                       "Internet Users",
                                       "Life Expectancy", 
                                       "Labor Force Participation", 
                                       "Military Spending", 
                                       "Murders rate"))) %>% 
kable(
  format = "latex",
  booktabs = TRUE,
  escape = FALSE,
  longtable = TRUE,
 caption = "Descriptive Statistics")
```
